Viability of FTIR on fossil pollen

### 2020-02-11 manuscript.Rmd
added references.bib; wrote notes on possible cores

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output: pdf_document
---

@@

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age

Notes:
- Time to measure 50 pollen grains on single taxa slides: min 60 min. 
- includes Mounting, selecting pollen, measuring time FTIR

>>>>

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  pdf_document: default
bibliography: references.bib
---

@@

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age
## Cores
Dalman Lado:

Totenmoos [@heissUltenValleySouth2005]:
- bog-sediment core
- min 1000 grains counted
- Picea, Pinus very common, switch at 10000 BP from Pinus to Picea
- Alnus, Betula throughout
- Abies, Fagus after 9000 BP
- trace Quercus

Younger Dryas [@brauerHighResolutionSediment1999]:
- 12 samples laminated sediment
- from  11400 to 13120
- min 500 grains
- pollen conc highest in 11000-11600 and 12700-12900
- Pinus betula most common (ca 150 grains counted)
- salix (ca 25 counted)
- quercus throughout in low conc (<1%)
- graminoids/cyperaceae/artemisia common

Tinner alpine:

Tinner meso-mediterranean:
Quercus sections Quercus, Cerris and Ilex

Tinner thermo-mediterranean:
Quercus sections Quercus, Cerris and Ilex

## Time to measure notes:
- Time to measure 50 pollen grains on single taxa slides: min 60 min. 
- includes Mounting, selecting pollen, measuring time FTIR
